---
title: "group_document.qmd"
format: html
editor: visual
---

# Lab 7 - Group 10

## Marie

We want to define x and y as two vectors for later use

```{r}

#defining x
x <- c(1,2,3,4,5,3)
x
#defining y
y <- c(9,7,6,5,4,3)
y
```

### New feature

No we try to multiply the vectors to get vector c:

```{r}
# Combining the vectors x and y
c <- x + y
c
```

## Amalie

Now It is time for the bestest part of the whole script

```{r}
GroupMembers <- c("Amalie","Johanna","Sofie","Marie","Malou")

Student_ids <- c("s204643","s203566","s203566","s203515","s204657","s194678")
```

### New Analysis

Here is my analysis of how this groupwork is going

```{r}
library(tidyverse)

who <- "I "
What <- "Think "
Verb <- "is "
Verb2 <- "going "
How <- "well"

str_c(who,What,Verb,Verb2,How)


```

## Johanna

### New Feature

**I like this** *what about you?*

-   Bullet point 1

-   bullet point 2

```{r}
kode <- "code"
```

Here is my code

```{r}
Hej <- 2+2
```

```{r}
code <- Hej
```

```{r}
1+1+1+1

```

## Sofie

Hej med jer.

Kode kommer her:

```{r}
1+1

```

```{r}
hej <- 10^2
```

## New feature

I will enter some next text, I did! Wuhu!

```{r}
hej1 <- hej*2
hej1
```

## Malou

Now we will add some changes to the document, so that we can update and see all other peoples changes. Here is a simple one:

```{r}
x <- 2+2
x
```

### New feature

This new feature is further opreations on x.

```{r}
y <- x^2 + x^3 + x^4
y
```
