------------------------------------------------------------------------

---
title: "Lab 7 Assignment: Group 10"
format: 
  html:
    embed-resources: true
editor: visual
---

## Lab 7 Group Assignment

**Group 10**

Johanna Haraldsdottir (s204657), Marie Kragh (s203566), Sofie Bruun (s194678), Amalie Schultz-Nielsen (s204643) and Malou Bech Jakobsen (s203515)

## Load data

```{r}
rm(list=ls())
library(tidyverse)
library(broom)
```

Here we load in the data

```{r}
# downloading the data 
target_url <- "https://github.com/ramhiser/datamicroarray/raw/master/data/gravier.RData"
output_file <- "data/gravier.RData"
curl::curl_download(url = target_url, destfile = output_file)
```

```{r}
# Loading the gravier into a list
load(output_file)

```

## Explanation of data

The Gravier dataset contains gene expression data from 168 patients with breast cancer. The data is used to classify the patients into two prognostic classes: "good" and "poor" prognosis based on their 5-year survival outcomes. The dataset features 2905 gene expression levels for each patient. 111 patients were labelled good and 57 patients were labelled poor.

## Data wrangling

**Cleaning data:**

```{r}
gravier_clean <- gravier |>
  bind_cols() |>
  as_tibble()
```

**Compressing the data:**

```{r}
# tsv is tab seperated

gravier_clean  |> 
  write_tsv(file = "data/02_gravier_clean.tsv.gz")
```

**Changing non-numeric variable:**

```{r}
gravier_clean_aug <- gravier_clean |>
  mutate(y = case_when(y == "poor" ~ 1,
                       y == "good" ~ 0)) |> 
  relocate(early_metastasis = y)
```

## Data Analysis

### Principal Component Analysis - PCA

```{r}
# we do the PCA on the numers in our dataframe which are numeric 

pca_fit <- gravier_clean_aug %>% 
  select(where(is.numeric)) %>% # retain only numeric columns
  prcomp(scale = TRUE) # do PCA on scaled data

```

### Investigating PC coordinates

```{r}
pca_fit %>%
  augment(gravier_clean_aug) %>% # add original dataset back in 
  ggplot(aes(.fittedPC1, .fittedPC2, color=as.factor(early_metastasis))) +
  geom_point() + 
  ggtitle('Principal components coordinats') +
  guides(color = guide_legend(title = "Early metastasis"))
  
```

### Evaluating the variance explained in each PC

We want to look at the principle components

```{r}
pca_fit |> 
  tidy(matrix = "eigenvalues")
```

Now I make the plot for the principle components that are explaining the variance in te gravier dataset

```{r}
pca_fit |> 
  tidy(matrix = "eigenvalues") |> 
  ggplot(aes(PC, percent)) +
  geom_col(fill = "#56B4E9", alpha = 0.8) +
  scale_x_continuous(breaks = 1:168) +
  scale_y_continuous(
    labels = scales::percent_format(),
    expand = expansion(mult = c(0, 0.01))
  ) 
```
