---
title: "Lab 7 Assignment: Group 10"
format: 
  html:
    embed-resources: true
editor: visual
---

## Lab 7 Group Assignment

**Group 10**

Johanna Haraldsdottir (s204657), Marie Kragh (s203566), Sofie Bruun (s194678), Amalie Schultz-Nielsen (s204643) and Malou Bech Jakobsen (s203515)

## Load data

```{r}
library(tidyverse)
```

Here we load in the data

```{r}

target_url <- "https://github.com/ramhiser/datamicroarray/raw/master/data/gravier.RData"
output_file <- "data/gravier.RData"
curl::curl_download(url = target_url, destfile = output_file)

```

## Data wrangling

**Cleaning data:**

```{r}
gravier_clean <- gravier |>
  bind_cols() |>
  as_tibble()
```

**Compressing the data:**

```{r}
# tsv is ta seperated

readr::write_tsv(x = gravier_clean, file = gzfile("data/02_gravier_clean.tsv.gz"))
```

**Changing non-numeric variable:**

```{r}
gravier_clean_aug <- gravier_clean |>
  mutate(y = case_when(y == "poor" ~ 1,
                       y == "good" ~ 0)) |> 
  relocate(early_metastasis = y)
```

## Data Analysis

### Investigating PC coordinates

### Principal Component Analysis - PCA

### Evaluating the variance explained in each PC
